毕业设计论文

### 2010-06-19 doc/paper/mypaper.tex
论文

Web服务器作为互联网的核心组成部分，在支撑整个互联网服务中，起到了至关重要的作用。由于互联网中应用的不断更新，要求web服务器也能适应这种更新变化。同时，web服务器必须保证7*24小时的运行。在目前的正在使用的web服务器中，大部分都不支持功能的动态增加，也就是在不重启服务器的情况下，动态的为服务器增加功能。针对这一问题，本课题基于动态链接库技术，使服务器在运行期间，可以动态的获知模块的增加并加载模块。

本论文的主要内容是研究实现基于动态链接技术的Web服务器动态加载插件的接口。首先，文中介绍了本课题的背景和意义，以及作者的主要任务和工作。接着概述与本课题相关的HTTP协议（RFC2616）的内容，简单介绍动态链接技术及其使用，还有介绍Web服务器的一些主流设计和实现方法。接下来，通过对HTTP协议的分析，设计插件的接口，分析动态链接技术，设计动态加载插件的过程。然后，采用非阻塞I/O+线程池+I/O多路复用技术，设计服务器的架构。然后，根据以上的设计，在Linux系统下，实现服务器的原型，并在其上实现插件接口和动态加载功能。本系统实现了服务器的基本功能，重点实现模块动态加载特性，并对实现进行测试。

@@

\section*{Comments}

@@

\begin{itemize}
\item Ed Hall posted a few notes on his experiences; he's achieved >1000 connects/second on a UP P2/333 running Solaris. His code used a small pool of threads (1 or 2 per CPU) each managing a large number of clients using "an event-based model".
\item Mike Jagdis posted an analysis of poll/select overhead, and said "The current select/poll implementation can be improved significantly, especially in the blocking case, but the overhead will still increase with the number of descriptors because select/poll does not, and cannot, remember what descriptors are interesting. This would be easy to fix with a new API. Suggestions are welcome..."
\item Mike posted about his work on improving select() and poll().
\item Mike posted a bit about a possible API to replace poll()/select(): "How about a 'device like' API where you write 'pollfd like' structs, the 'device' listens for events and delivers 'pollfd like' structs representing them when you read it? ... "
\item Rogier Wolff suggested using "the API that the digital guys suggested", \\http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps
\item Joerg Pommnitz pointed out that any new API along these lines should be able to wait for not just file descriptor events, but also signals and maybe SYSV-IPC. Our synchronization primitives should certainly be able to do what Win32's WaitForMultipleObjects can, at least.
\item Stephen Tweedie asserted that the combination of F\_SETSIG, queued realtime signals, and sigwaitinfo() was a superset of the API proposed in http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps. He also mentions that you keep the signal blocked at all times if you're interested in performance; instead of the signal being delivered asynchronously, the process grabs the next one from the queue with sigwaitinfo().
\item Jayson Nordwick compared completion ports with the F\_SETSIG synchronous event model, and concluded they're pretty similar.
\item Alan Cox noted that an older rev of SCT's SIGIO patch is included in 2.3.18ac.
\item Jordan Mendelson posted some example code showing how to use F\_SETSIG.
\item Stephen C. Tweedie continued the comparison of completion ports and F\_SETSIG, and noted: "With a signal dequeuing mechanism, your application is going to get signals destined for various library components if libraries are using the same mechanism," but the library can set up its own signal handler, so this shouldn't affect the program (much).
\item Doug Royer noted that he'd gotten 100,000 connections on Solaris 2.6 while he was working on the Sun calendar server. Others chimed in with estimates of how much RAM that would require on Linux, and what bottlenecks would be hit.
\end{itemize}
Interesting reading!

\chapter{附录二： c10k问题}
	现在的web服务器同时要处理上万个客户端，你不这样认为么？毕竟，现在互联网是一个强大的地方。

@@

	有趣的文章！

>>>>

Web服务器作为互联网的核心组成部分，在支撑整个互联网服务中，起到了至关重要的作用。由于互联网中应用的不断更新，要求web服务器也能适应这种更新变化。同时，web服务器必须保证7*24小时的运行。在目前的正在使用的web服务器中，大部分都不支持功能的动态增加，也就是在不重启服务器的情况下，动态的为服务器增加功能。

本论文的主要内容是研究实现基于动态链接技术的Web服务器动态加载插件的接口。首先，文中介绍了本课题的背景和意义，以及作者的主要任务和工作。接着概述与本课题相关的HTTP协议（RFC2616）的内容，简单介绍动态链接技术及其使用，还有介绍Web服务器的一些主流设计和实现方法。接下来，通过对HTTP协议的分析，设计插件的接口，分析动态链接技术，设计动态加载插件的过程。然后，采用非阻塞I/O+线程池+I/O多路复用技术，设计服务器的架构。本系统实现了服务器的基本功能，重点实现模块动态加载特性，并对实现进行测试。

@@

\section{Comments}

@@

\begin{itemize}
\item Ed Hall posted a few notes on his experiences; he's achieved >1000 connects/second on a UP P2/333 running Solaris. His code used a small pool of threads (1 or 2 per CPU) each managing a large number of clients using "an event-based model".
\item Mike Jagdis posted an analysis of poll/select overhead, and said "The current select/poll implementation can be improved significantly, especially in the blocking case, but the overhead will still increase with the number of descriptors because select/poll does not, and cannot, remember what descriptors are interesting. This would be easy to fix with a new API. Suggestions are welcome..."
\item Mike posted about his work on improving select() and poll().
\item Mike posted a bit about a possible API to replace poll()/select(): "How about a 'device like' API where you write 'pollfd like' structs, the 'device' listens for events and delivers 'pollfd like' structs representing them when you read it? ... "
\item Rogier Wolff suggested using "the API that the digital guys suggested", \\http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps
\item Joerg Pommnitz pointed out that any new API along these lines should be able to wait for not just file descriptor events, but also signals and maybe SYSV-IPC. Our synchronization primitives should certainly be able to do what Win32's WaitForMultipleObjects can, at least.
\item Stephen Tweedie asserted that the combination of F\_SETSIG, queued realtime signals, and sigwaitinfo() was a superset of the API proposed in http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps. He also mentions that you keep the signal blocked at all times if you're interested in performance; instead of the signal being delivered asynchronously, the process grabs the next one from the queue with sigwaitinfo().
\item Jayson Nordwick compared completion ports with the F\_SETSIG synchronous event model, and concluded they're pretty similar.
\item Alan Cox noted that an older rev of SCT's SIGIO patch is included in 2.3.18ac.
\item Jordan Mendelson posted some example code showing how to use F\_SETSIG.
\item Stephen C. Tweedie continued the comparison of completion ports and F\_SETSIG, and noted: "With a signal dequeuing mechanism, your application is going to get signals destined for various library components if libraries are using the same mechanism," but the library can set up its own signal handler, so this shouldn't affect the program (much).
\item Doug Royer noted that he'd gotten 100,000 connections on Solaris 2.6 while he was working on the Sun calendar server. Others chimed in with estimates of how much RAM that would require on Linux, and what bottlenecks would be hit.
\end{itemize}
\chapter{附录二： c10k问题}
	现在的web服务器同时要处理上万个客户端，你不这样认为么？毕竟，现在互联网是一个强大的地方。

@@
